\rule{\textwidth}{4pt}\\ \textbf{From Distribution Forecasts to Vanilla Portfolios: \\[0.2cm] Regularized Payout Approximation in Discrete Space}\\[0.2cm] \rule{\textwidth}{2pt}

### 2025-02-12 latex/article.tex
figure

\keywords{
    \small{
        Vanilla Options, 
        Payout Profile, 
        Financial Engineering, 
        Option Pricing, 
        Approximation, 
        Numerical Methods,
        Quantitative Finance,
        Financial Derivatives,
        Computational Finance,
        Distribution Forecasts,
        Portfolio Construction,
        Option Trading
    }
}

@@

@@

\begin{figure}[htbp]
\centering
\input{regularization_comparison.tex}
\caption{Comparison of regularization methods using 9 strike prices.}
\label{fig:regularization}
\end{figure}

>>>>

\keywords{
    \small{
        Vanilla Options, 
        Payout Profile, 
        Financial Engineering, 
        Option Pricing, 
        Approximation, 
        Numerical Methods,
        Quantitative Finance,
        Financial Derivatives,
        Computational Finance,
        Distribution Forecasts,
        Option Trading
    }
}

@@

\begin{figure}[htbp]
\centering
\input{regularization_comparison.tex}
\caption{Comparison of L1 and L2 regularization}
\label{fig:regularization}
\end{figure}

Figure~\ref{fig:regularization} demonstrates the effectiveness of both regularization approaches in approximating a complex payout profile. The target function combines linear, sinusoidal, and power-law segments, presenting a challenging test case. Both methods achieve good approximation quality, with L2 regularization providing slightly smoother results and L1 regularization favoring a sparser representation with fewer non-zero option weights.

@@

### 2025-02-12 latex/regularization_comparison.tex
figure

\begin{tikzpicture}
\begin{axis}[
    width=0.9\textwidth,
    height=6cm,
    grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt,draw=gray!50},
    xlabel style={font=\tiny},
    ylabel style={font=\tiny},
    tick label style={font=\tiny},
    title style={font=\small},
    legend style={font=\tiny, at={(0.02,0.98)}, anchor=north west},
    xlabel={Underlying Asset Price},
    ylabel={Payout},
    title={Regularization Methods Comparison}
]

>>>>

\begin{tikzpicture}
\begin{axis}[
    width=0.9\textwidth,
    height=6cm,
    grid=both,
    grid style={line width=.1pt, draw=gray!10},
    major grid style={line width=.2pt,draw=gray!50},
    xlabel style={font=\tiny},
    ylabel style={font=\tiny},
    tick label style={font=\tiny},
    title style={font=\small},
    legend style={font=\tiny, at={(0.02,0.98)}, anchor=north west},
    xlabel={Underlying Asset Price at Maturity},
    ylabel={Payout},
    title={Regularization Methods Comparison}
]
